ms_figures

### 2018-01-24 analysis/chronos/analysis_splines.Rmd
update figures

# Export data 
write.csv(cro_rwi, file=paste(di, "data/cronos_medias/cronos_sites_rwi.csv", sep=""), row.names = FALSE)
```

@@

year_sampledepth <- year_sampledepth %>% 
  mutate(site_sorted = case_when(
    site == "sj" ~ "0_sj", 
    site == "caH" ~ "1_caH",
    site == "caL" ~ "2_caL"))
```

>>>>

# Export data 
# write.csv(cro_rwi, file=paste(di, "data/cronos_medias/cronos_sites_rwi.csv", sep=""), row.names = FALSE)
```

@@

year_sampledepth <- year_sampledepth %>% 
  mutate(site_sorted = case_when(
    site == "sj" ~ "0_sj", 
    site == "caH" ~ "1_caH",
    site == "caL" ~ "2_caL"))

# Export data 
write.csv(cro_rwi, file=paste(di, "data/cronos_medias/cronos_sites_rwi.csv", sep=""), row.names = FALSE)
write.csv(year_cutoffs, file=paste(di, "data/cronos_medias/cronos_sites_rwi_year_cutoffs.csv", sep=""), row.names = FALSE)
write.csv(year_sampledepth, file=paste(di, "data/cronos_medias/cronos_sites_rwi_year_sampledepth.csv", sep=""), row.names = FALSE)
```

### 2018-01-24 man/ms_figures.Rmd
update figures

![](../analysis/chronos/analysis_chronologies_files/figure-markdown_github/crono_compara_sitesSJCALH-1.png)

Figure 5. Basal Area Increment (BAI) chronologies of *Q. pyrenaica* for northern population (SJ; *green*) and southern ones: low-elevation (CA_Low; *pink*) and high-elevation (CA_High, *purple*) sites. Shading areas coorespond to standard error of the mean.

@@

>>>>

@@

Figure 5. Basal Area Increment (BAI) chronologies of *Q. pyrenaica* for northern population (SJ; *green*) and southern ones: low-elevation (CA_Low; *pink*) and high-elevation (CA_High, *purple*) sites. Shading areas coorespond to standard error of the mean. Number of series are displayed in the upper plot.

# Figure 6

```{r}
cro_rwi <- read.csv(here("data/cronos_medias", "cronos_sites_rwi.csv"), header = TRUE, sep = ',')
year_cutoffs <- read.csv(here("data/cronos_medias", "cronos_sites_rwi_year_cutoffs.csv"), header = TRUE, sep = ',')
year_sampledepth <- read.csv(here("data/cronos_medias", "cronos_sites_rwi_year_sampledepth.csv"), header = TRUE, sep = ',')

label_site <- c("0_sj" = "Northern (SJ)",
                "1_caH" = "Southern High (CaH)",
                "2_caL" = "Southern Low (CaL)")

# 
plot_rwi_crono <- ggplot(cro_rwi, aes(x=year, y=res)) +
  theme_bw() + 
  theme(panel.grid = element_blank(), 
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face="bold", size=12), 
        axis.text = element_text(face="bold", size=10), 
        axis.title = element_text(face="bold", size=12)) + 
  geom_hline(yintercept = 1, colour = "grey") + 
  geom_line(size=.8) + scale_y_continuous(breaks = seq(0.4,1.8, 0.2)) +
  facet_wrap(~site_sorted, scales = "fixed", ncol = 1,
             labeller = as_labeller(label_site)) + 
  ylab("Ring width index") + xlab("Year") + 
  geom_vline(xintercept = c(1995, 2005, 2012), linetype = "dotted") + 
  geom_vline(aes(xintercept = year), data = year_cutoffs,  linetype = "dashed", colour='red') + 
  geom_vline(aes(xintercept = year), data = year_sampledepth,  linetype = "dashed", colour='blue') +
  scale_x_continuous(limits = c(1819, 2016), 
                     breaks= seq(1820, 2020, by=20))

plot_rwi_crono
